Documentation FFI Sonar Simulator

### 2013-05-23 FFI-Simulator/ffi-simulator.tex
la2pdf commit - 2013:05:23	15:21:25	(Thu23.May)

But can we accurately simulate a sonar system using a framework designed to simulate optics?

@@

\begin{figure}[b]
\begin{minipage}[c]{0.49\linewidth}
\graphicsAI[drawing,width=\linewidth]{gfx/simulation_mask.png}
\centering\itshape Simulation mask
\end{minipage}\mbox{}\hfill
\begin{minipage}[c]{0.49\linewidth}
\graphicsAI[drawing,width=\linewidth]{gfx/simulation_object.png}
\centering\itshape Simulated object
\end{minipage}
\graphicsAI[drawing,width=\linewidth]{gfx/simulation_optical.png}
\centering\itshape Combined image\vspace{5pt}
\caption{Optical rendering.}\label{s}
\end{figure}

@@

Are such an approach accurate enough? Or do we need to consider layover, multipath, or other effects as well?

@@

If layover and multipath are important, then the techniques used to simulate the previous images can not be used. A CUDA / OpenCL implementation can handle this. but no implementation is best at everything. but how these should be designed depends on the effects we wish to implement. For layover one could launch a thread for each pixel in the image, let it find all the points in the image that contributes with direct returns to that pixel, and sum the contributions up. For multipath a ray tracer customized for sound is likely the better option.

>>>>

But can we accurately simulate a sonar system using a framework designed to simulate optics? We did a quick simulation to get a feel for this.

@@

\begin{figure}[b]
\begin{minipage}[c]{0.49\linewidth}
\graphicsAI[drawing,width=\linewidth]{gfx/simMask0001.png}
\centering\itshape Simulation mask
\end{minipage}\mbox{}\hfill
\begin{minipage}[c]{0.49\linewidth}
\graphicsAI[drawing,width=\linewidth]{gfx/simObject0001.png}
\centering\itshape Simulated object
\end{minipage}
\graphicsAI[drawing,width=\linewidth]{gfx/simScene0001.png}
\centering\itshape Combined image\vspace{5pt}
\caption{Optical rendering.}\label{s}
\end{figure}

@@

Is such an approach accurate enough? Or do we need to consider layover, multipath, or other effects as well?

@@

If layover and multipath are important, then the techniques used to simulate the previous images can not be used. A CUDA / OpenCL implementation can handle this, but no implementation is best at everything. but how these should be designed depends on the effects we wish to implement. For layover one could launch a thread for each pixel in the image, let it find all the points in the image that contributes with direct returns to that pixel, and sum the contributions up. For multipath a ray tracer customized for sound is likely the better option.
